Approximate Code: A Cost-Effective Erasure Coding Framework for Video Applications in Cloud Storage Systems

### 2019-04-16 ApproximateCode.tex
version 3.6

\title{Approximate Code: A Cost-Effective Erasure Code for Video Applications in Cloud Storage Systems}

@@

\begin{abstract}
Multimedia data generated by autonomous driving, media industry and security monitoring is often stored in cloud storage systems and occupies a large amount of space. Meanwhile, to ensure the data reliability, distributed file systems often use erasure codes to backup data. However, the commonly used triple disk failure tolerant arrays (3DFTS) erasure code scheme is expensive, not only because simultaneous damage of multiple disks is relatively rare, but also due to its ignorance of redundant information inside the data, resulting in multiple complete parity disks being excessive. On the other hand, the recently proposed approximate storage scheme can effectively reduce storage costs, but at the cost of sacrificing the reliability of some data.

In this article, we propose Approximate Code for multimedia applications, which is an erasure code using an approximation strategy. Approximate Code aims to ensure different reliability of important and unimportant data by means of erasure coding, thereby reducing storage overhead. It provides complete recovery when fewer disks fail, and ensures approximate recovery (recover most data) in the event of multiple disk failures. To demonstrate the effectiveness of Approximate Code, we conduct several experiments in Hadoop and Alibaba Cloud systems. 
The results show that compared with the typical high-reliability erasure code schemes, Approximate Code significantly reduces reduce the storage overhead and provide high reliability of important data.

@@

Although multiple replicas can be used to ensure data availability and reliability, this method is too expensive and is only used to save hot data in practice. In contrast, the amount of cold data is far more than hot data, and erasure code (EC) schemes are ideal for storing such data. It provides lower storage overhead and write bandwidth than replication with the same fault tolerance. Currently, many cloud storage systems use erasure code to tolerate disk failures and ensure data availability, such as Windows [], Amazon AWS [] or Alibaba Cloud []. Typical erasure codes configuration use three-disk fault tolerant array (3DFTS). However, its overhead is still too high because the simultaneous damage of triple disks is relatively rare.

The recently proposed approximate storage strategy can significantly reduce the consumption of storage resources and energy. Common methods are to ensure the reliability of important data while storing the unimportant data on relatively unreliable media or reducing their error correction coding. Multimedia data is a typical application scenario for approximate storage because they can tolerate data corruption compared to other data. For example, video data records at least 20 frames per second, which makes it difficult for a typical user to perceive the loss of several frames. Also, some pixel errors in the image data do not affect the information of the entire picture. However, the direct application of approximate storage in a cloud storage system will result in the unimportant data being unacceptable volatile.

@@

First, existing erasure codes generally reach or exceed 3DFTS, and use more than 3 parity disks. However, the simultaneous damage of 3 disks is very rare, and the storage overhead paid for this is too large. Second, the existing erasure codes provide the same fault tolerance for all data without distinction, which results in the same reliability of important data that is sensitive to errors and data that is robust. Last but not least, the current approximate storage methods are unreliable since they are not designed to tolerate disk level failure.

@@

\subsection{Design of Approximate Code}
The construction of the Approximate Code is determined by 5 parameters $k$, $r$, $h$, $g$ and $s$.

First, we use Figure \ref{fig-chunk-block} to illustrate the term \emph{chunk}, \emph{block}, \emph{stripe} and \emph{layer} we use in this paper. In a system of $n$ nodes, $k$ of them are data nodes and $r=n-k$ nodes are for parity. Each node can be divided into multiple blocks. We focus on the $s$ blocks of the same logical position of each node, and we treat these $s$ nodes as a \emph{chunk}. The $n$ chunks constitute a \emph{stripe}. Approximate Code are designed for $h$ stripes, where each stripe can be in the same $n$-node system, or on different $n$-node systems.
For the latter situation, we specifically use \emph{layer} instead of stripe, since these two cases will result in different performance and reliability.

For $s$ blocks in each chunk, we assume that important data occupies 1 block, so the ratio of unimportant data to important data is $a-1$.
In addition, there is another $g$ global chunks, which are calculated only by the important data blocks. It should be point out that $g$ global parity chunks should be placed in $g$ different nodes and should be different from the data nodes. 
The number of important data block is $h \times k$, and they generate $h \times g$ global parity blocks.

To sum up, the number of blocks involved in the approximate code is 
$$((k+r)s + g) \times h$$

Approximate Code guarantees that for each stripe, the unimportant data can tolerate any $r$ node failures. Usually, $r$ is equal to 1 or 2, which covers most node failure scenarios. Important data are provided $r+g$ node failure tolerance, and $g$ is usually configured as $3-r$ to achieve tipical 3DFTS.

The construction of Approximate Code (4,1,4,2,5) can be illustrated by Figure \ref{fig-ap-41425}, where $N_i$ are data nodes, $P_{i}$ are local parity nodes and $G_i$ are global parity chunks. 
This example includes 22 nodes.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.35\textwidth]{photo/AP-kmha-v5.pdf}
\caption{A sample of Approximate Codes $(4,1,4,2,5)$ with $h=4$ layers of nodes, where each layer contains $k=4$ data nodes (marked as water green) and $r=1$ parity nodes(marked as orange).
The important data (marked as blue) occupies $1/5$ of the total data node, and generate $g=2$ global parity chunks (marked as red).}
\label{fig-ap-41425}
\end{figure}

\iffalse
\subsection{Encoding and Decoding Process}
\subsubsection{Encoding Process}
The encoding process of Approximate Code is simple, which can be divided into 2 parts: local and global.
The local encoding process takes place in the stripe, where data are encoded in node level. In fact, EC methods such as RS-based, XOR-based, MSR, MDS or PMDS codes can all be used to construct the local parity nodes for different advantages.
The global encoding process is only for important data. It is designed to encode important data across stripes. There are also several ways to implement it.
\subsubsection{Decoding Process}
Approximate Code decodes important and unimportant data in different ways. Since the unimportant data is only encoded in local way, its decoding process is on the contrary.
The important data is encoded in both local and global ways, so all the local and global parity chunks are used to decode it, which can be divided into 3 steps:
\begin{enumerate}
\item Inter-layer check, reconstruct data using global parity chunks until it exceeds fault tolerance.
\item In-layer check, reconstruct data using local parity chunks until it exceeds fault tolerance.
\item Inter-layer check again, reconstruct using the global parity chunks.
\end{enumerate}

\subsection{Recovery Mode}
\subsubsection{Full Recovery Mode}
In general, our parameter settings guarantee $h<k$, so the global parity chain is shorter than the local one and has a lower reconstruct overhead.
In addition, the global parity chunks are encoded by XOR, which results in high decoding speed.
Therefore, important data blocks tend to recover data using global parity blocks whenever possible, which makes the Approximate Code have low overall computational overhead and reconstruction costs in \emph{full recovery mode}.
\subsubsection{Approximate Recovery Mode}
\fi

\subsection{RS-based Approximate Code}
We still use Figure \ref{fig-ap-41425} to illustrate RS-based Approximate Code $(4,1,4,2,5)$ and its properties. The local parity chunks are encoded by RS(4,1), and the important data generate another 2 global parity chunks. It is easy to find appropriate coefficient to ensure important data forms the form of RS(4,3) and tolerate any 3 chunk failure. Figure \ref{fig-ap-rs} shows the generate matrix of Layer 0 in Figure \ref{fig-ap-41425}.

\begin{figure}[h]
\centering
\includegraphics[width=0.45\textwidth]{photo/AP-RS-43.pdf}
\caption{The generate matrix of RS-based Approximate Codes $(4,1,4,2,5)$, where $ID_i$ and $UD_i$ represnt the important and unimportant data in $N_i$. $G_0$ and $G_1$ are the parity blocks corresponding to important data blocks.}
\label{fig-ap-rs}
\end{figure}

\subsection{XOR-based Approximate Code}
We introduce the construction of XOR-based Approximate Code $(4,1,4,2,5)$ and Approximate Code $(4,1,4,2,5)$

Since we mainly provide 3DFTS for important data, we prefer to construct Approximate Code with several RAID6-based codes to provide faster encoding and reconstruction speed than RS.

\begin{figure}[h]
\centering
\includegraphics[width=0.4\textwidth]{photo/AP-TIP.pdf}
\caption{The generate matrix of RS-based Approximate Codes $(4,1,4,2,5)$, where $ID_i$ and $UD_i$ represnt the important and unimportant data in $N_i$. $G_0$ and $G_1$ are the parity blocks corresponding to important data blocks.}
\label{fig-ap-TIP}
\end{figure}

\iffalse
\subsection{Fault Tolerance}
In this section we give the fault tolerance of important and unimportant data in the Approximate Code.
We first prove the correctness of our decoding process, and then use a program to 
iterate through all the cases of node failures. Finally, we give the data recovery capability of all cases.

For unimportant data, it only has local parity nodes, so its fault tolerance in Approximate Code($k,r,h,a$) is the same as RS($k,r$), which is any $r$ node failures in $k+r$ nodes in each layer.

For important data, We consider the \emph{full recovery mode} and the \emph{approximate recovery mode} separately. When the number of nodes lost per layer does not exceed $r$, the Approximate Code completely recovers all data in \emph{full recovery mode}. If the damage is more severe, the Approximate Code enters the \emph{approximate recovery mode}.

We still take the Approximate Code ($3, 2, 2, 1/3$) as an example, and discuss the fault tolerance of important and mionor data separately.

Important data nodes can tolerate the loss of any 2r+1 data nodes
At the same time tolerate any r+1 node loss. Only in very rare cases, r+2 nodes are damaged in this way, that is, a data node whose local check node and global check node are damaged at the same time.

First consider only the data nodes:
Second, for the case of all nodes:
\fi

\iffalse
\subsection{Reconstruct Cost}
In this section, we introduce the recovery overhead for several common failure cases of Approximate Code. The reconstruct cost is defined as the 
\subsubsection{Single node failure}
When any one data node fails, the reconstruction cost of unimportant data is $k$ read and 1 write, while important data has the cost of $h$ read and 1 write. So the total amount of data that needs to be transferred is 
$$ (1-a)*(k+1) + a*(h+1) $$.

@@

\begin{table}[ht]
\centering 
\caption{Comparison of storage overhead and reconstruction cost between Approximate Code, RS and RAID-6.}\label{tab-AS-RS-AP}
\begin{tabular}{|c|c|c|}
\hline
EC & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}Reconstruction Cost\\ (single data node failure)\end{tabular} \\ \hline
RS($k,r$) & $\frac{k+r}{k}$ & $k$ \\ \hline
RAID-6($k,2$) & $\frac{k+2}{k}$ & $k$ \\ \hline
\begin{tabular}[c]{@{}c@{}}Ap-Code\\ ($k,r,h,a$)\end{tabular} & $\frac{(k+r)h+ak}{kh}$ & $(1-a)*(k+1) + a*(h+1)$ \\ \hline
\end{tabular}
\end{table}

@@

We analyze the nature of the Approximate Code from the following aspects, and the calculation method of the relevant indicators is given in Table \ref{tab-AS-RS-AP}.
\begin{itemize}
    \item Low cost. Approximate code reduces storage overhead by approximating storage strategies. This property is more pronounced for data with a smaller proportion of important data.
    \item High reliability for important data. The Approximate Code guarantees the fault tolerance of the important data $m+s$.
    \item Flexibility. The implementation of the Approximate Code can be based on RS, XOR or a mixture of the two; at the same time, the construction of the Approximate Code can also be used for encoding such as LRC or MSR.
\end{itemize}

\section{Implementation}\label{Implementation}

\begin{figure}[htb]
\centering
\includegraphics[width=0.4\textwidth]{photo/implementation.pdf}
\caption{Overview of Approximate Code implementation}
\label{fig-implementation}
\end{figure}

Compared with the traditional scheme that does not consider the meaning of the upper layer data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate layer between the upper layer application and the underlying distributed storage system is necessary to preprocess the data. We call it the approximate storage layer.
The approximate storage layer is responsible for the identification and allocation of data. It controls the EC module and implements the encoding and decoding work of the Approximate Code.

\subsection{Data Identification}
The identification of data importance can be specified by the upper application as well as automatically determined by the approximate storage layer. We focus on the latter and take video file as an example to introduce our method of automatically distinguishing importance.

For video data encoded by H.264 or similar format, we define I frames as important data, while P frames and B frames as unimportant data based on the analysis in section \ref{video storage}. In practical, video data is rarely stored in the original form of H.264 streams (``.264'' files), but is usually storaged in an file such as ``.mp4'' files containing information such as audio. We transcode video files into raw video streams and other data, and we define these non-video data as important because they contain information that the video can't provide and only take up a small amount of space. The feasibility of this definition will be confirmed in \ref{evaluation}.

@@

The data distribution scheme is shown in the figure \ref{Data-distribution-v2}. We present $\omega_i$ as the $\omega$ of Data(i), and $\omega_{max} = \omega_2$.
For example, Data 3 is represnted by blue, and its key segment (10\%) and part of unimportant segment (10\%) are settled in $D_I$.
The main idea of our data distribution method is to guarantee that each GOP has the same proportion of storage in $D_I$ and $D_M$. This method improves flexibility because it is not necessary to maintain a map that marks the location of each GOP, which makes it is easy to add or delete data at any time. Meanwhile, the method is ideal for streaming video data generated in real time by applications such as monitoring.

@@

\subsection{Evaluation methodology}
In our evaluation, we first compare the Approximate Code with the RS code and some XOR-based codes to demonstrate the performance benefits of our solution. Since 3DFTS is a typical erasure code configuration, we use it as a baseline and set the minimum fault tolerance of important data to 3 ($ m + s \geqslant 3 $). We will then demonstrate the quality loss of multimedia data under the traditional and approximate recovery models of severe disk failure to assess the benefits of our approximate storage scheme. We use mathematical analysis and experiments to prove the effectiveness of the Approximate Code.

>>>>

\title{Approximate Code: A Cost-Effective Erasure Coding Framework for Video Applications in Cloud Storage Systems}

@@

\begin{abstract}
Nowadays massive video data are stored in cloud storage systems, which are generated by various applications such as autonomous driving, news media, security monitoring, etc. Meanwhile, erasure coding is a popular technique in cloud storage to provide both high reliability with low monetary cost, where triple disk failure tolerant arrays (3DFTs) is a typical choice. Therefore, how to minimize the storage cost of video data in 3DFTs is challenge for cloud storage systems. Although there are several solutions like approximate storage technique for storage devices, it cannot guarantee low storage cost and high data reliability in storage systems concurrently.

To address this problem, in this paper, we propose Approximate Code, which is an erasure coding framework for video applications in cloud storage systems. The key idea of Approximate Code is distinguishing the important data and unimportant data in videos with different capabilities of fault tolerance. On one hand, for important data, Approximate Code provides triple parities to provide high reliability. On the other hand, single/double parities are applied for unimportant data, which can save the storage cost and accelerate the recovery process. To demonstrate the effectiveness of Approximate Code, we conduct several experiments in Hadoop systems. The results show that, compared to traditional 3DFTs using various erasure codes such as RS, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 60\%, saves the storage cost by up to 10\%, increase the recovery speed by up to 1.5X when single disk fails, and can reconstruct the whole video data via fuzzification when triple disks fail.

@@

Although multiple replicas can be used to ensure data availability and reliability, this method is too expensive and is only used to save hot data in practice. In contrast, the amount of cold data is far more than hot data, and erasure code (EC) schemes are ideal for storing such data. It provides lower storage overhead and write bandwidth than replication with the same fault tolerance. Currently, many cloud storage systems use erasure code to tolerate disk failures and ensure data availability, such as Windows [], Amazon AWS [] or Alibaba Cloud []. Typical erasure codes configuration use three-disk fault tolerant array (3DFTs). However, its overhead is still too high because the simultaneous damage of triple disks is relatively rare.

The recently proposed approximate storage strategy can significantly reduce the consumption of storage resources and energy. Common methods are to ensure the reliability of important data (marked as ID) while storing the unimportant data (marked as UD) on relatively unreliable media or reducing their error correction coding. Multimedia data is a typical application scenario for approximate storage because they can tolerate data corruption compared to other data. For example, video data records at least 20 frames per second, which makes it difficult for a typical user to perceive the loss of several frames. Also, some pixel errors in the image data do not affect the information of the entire picture. However, the direct application of approximate storage in a cloud storage system will result in the unimportant data being unacceptable volatile.

@@

First, existing erasure codes generally reach or exceed 3DFTs, and use more than 3 parity disks. However, the simultaneous damage of 3 disks is very rare, and the storage overhead paid for this is too large. Second, the existing erasure codes provide the same fault tolerance for all data without distinction, which results in the same reliability of important data that is sensitive to errors and data that is robust. Last but not least, the current approximate storage methods are unreliable since they are not designed to tolerate disk level failure.

@@

\subsection{Design of Approximate Code}
The construction of the Approximate Code is determined by 4 parameters $k$, $r$, $h$ and $s$. 
We use Figure \ref{fig-chunk-block} to illustrate the term \emph{chunk}, \emph{block}, \emph{stripe} and \emph{layer} we use in this paper. In a system of $n$ nodes, $k$ of them are data nodes and $r=n-k$ nodes are for parity. Each node can be divided into multiple blocks. We focus on the $s$ blocks of the same logical position of each node, and we treat these $s$ nodes as a \emph{chunk}. The $n$ chunks constitute a \emph{stripe}. Approximate Code are designed for $h$ stripes, where each stripe can be in the same $n$-node system, or on different $n$-node systems.
For the latter situation, we specifically use \emph{layer} instead of stripe, since these two cases will result in different performance and reliability.

For $s$ blocks in each chunk, we assume that important data occupies 1 block, so the ratio of important data to the whole chunk is $1/s$.
In addition, there are another $3-r$ global chunks, which are calculated only by the important data blocks. It should be point out that the global parity chunks should be placed in several different nodes and should be different from the data nodes. 
The number of important data block is $h \times k$, and they generate $h \times g$ global parity blocks.
To sum up, the number of blocks involved in the approximate code is 
$$((k+r)s + 3-r) \times h$$

Approximate Code guarantees that for each stripe, the unimportant data can tolerate any $r$ node failures. Usually, $r$ is equal to 1 or 2, which covers most node failure scenarios, while important data are provided 3DFTs.

The construction of Approximate Code (4,1,4,3) can be illustrated by Figure \ref{fig-ap-41425}, where $N_i$ are data nodes, $P_{i}$ are local parity nodes and $G_i$ are global parity chunks. 
This example includes 22 nodes.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.35\textwidth]{photo/AP-kmha-v6.pdf}
\caption{A sample of Approximate Codes $(4,1,4,3)$ with $h=4$ layers of nodes, where each layer contains $k=4$ data nodes (marked as water green) and $r=1$ parity nodes(marked as orange).
The important data (marked as blue) occupies $1/5$ of the total data node, and generate 2 global parity chunks (marked as red).}
\label{fig-ap-41425}
\end{figure}

\iffalse
\subsection{Encoding and Decoding Process}
\subsubsection{Encoding Process}
The encoding process of Approximate Code is simple, which can be divided into 2 parts: local and global.
The local encoding process takes place in the stripe, where data are encoded in node level. In fact, EC methods such as RS-based, XOR-based, MSR, MDS or PMDS codes can all be used to construct the local parity nodes for different advantages.
The global encoding process is only for important data. It is designed to encode important data across stripes. There are also several ways to implement it.
\subsubsection{Decoding Process}
Approximate Code decodes important and unimportant data in different ways. Since the unimportant data is only encoded in local way, its decoding process is on the contrary.
The important data is encoded in both local and global ways, so all the local and global parity chunks are used to decode it, which can be divided into 3 steps:
\begin{enumerate}
\item Inter-layer check, reconstruct data using global parity chunks until it exceeds fault tolerance.
\item In-layer check, reconstruct data using local parity chunks until it exceeds fault tolerance.
\item Inter-layer check again, reconstruct using the global parity chunks.
\end{enumerate}
\subsection{Recovery Mode}
\subsubsection{Full Recovery Mode}
In general, our parameter settings guarantee $h<k$, so the global parity chain is shorter than the local one and has a lower reconstruct overhead.
In addition, the global parity chunks are encoded by XOR, which results in high decoding speed.
Therefore, important data blocks tend to recover data using global parity blocks whenever possible, which makes the Approximate Code have low overall computational overhead and reconstruction costs in \emph{full recovery mode}.
\subsubsection{Approximate Recovery Mode}
\fi

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{photo/AP-RS-43.pdf}
\caption{The generate matrix of RS-based Approximate Codes $(4,1,4,3)$, where $ID_i$ and $UD_i$ represent the important and unimportant data in $N_i$. $G_0$ and $G_1$ are the parity blocks corresponding to important data blocks.}
\label{fig-ap-rs}
\end{figure}

\subsection{RS-based Approximate Code}
We still use Figure \ref{fig-ap-41425} to illustrate RS-based Approximate Code $(4,1,4,3)$ and its properties. The local parity chunks are encoded by RS(4,1), and the important data generate another 2 global parity chunks. It is easy to find appropriate coefficient to ensure important data forms the form of RS(4,3) and tolerate any 3 chunk failure. Figure \ref{fig-ap-rs} shows the generate matrix of Layer 0 in Figure \ref{fig-ap-41425}.

\subsection{XOR-based Approximate Code}
Since we mainly provide 3DFTs for important data, we prefer to construct Approximate Code with several RAID6-based codes to provide faster encoding and reconstruction speed than RS. This section introduce tipical cases of the construction of XOR-based Approximate Code ($5,1,6,6$) and $(4,2,4,4)$.

\subsubsection{RAID5-TIP Approximate Code}
\begin{figure}[h]
\centering
\includegraphics[width=0.35\textwidth]{photo/AP-TIP-v2.pdf}
\caption{The XOR-based Approximate Code ($5,1,6,6$), constructed based on RAID5 and TIP-code.}
\label{fig-ap-TIP}
\end{figure}

Figure \ref{fig-ap-TIP} is a tipical construction of Approximate Code ($5,1,6,6$) based on RAID5 and TIP-code \cite{zhang2015tip}. RAID5 tolerate one node failure while TIP-code is an XOR-based 3DFTs code. In each layer, local parity blocks provide horizontal XOR parity, and between layers, global parity provide diagonal parity and anti-diagonal parity.

The local (horizontal) parity elements are calculated by the following encoding equations.
\begin{align}
    LP_{i,0} &= \bigoplus_{j=0}^{k-1} ID_{i,j} (0 \leqslant i < h)\\
    LP_{i,p}(0<p<s) &= \bigoplus_{j=k(p-1)}^{kp-1} UD_{i,j} (0 \leqslant i < h)
\end{align}

When generating global parity blocks, the important data block, the local parity block, and the global parity block should be arranged as the encoding form of TIP-code. Figure \ref{fig-TIP} shows the coding method of diagonal and anti-diagonal parity blocks.
Since the encoding process of important data blocks can be seen as RAID5 plus TIP-code, it is obvious that they achieve 3DFTs.

\begin{figure}[h]
\subfigure[Diagonal parity $GP_0$ to $GP_5$, (e.g., $GP_0=ID_{0,0} \oplus ID_{1,4} \oplus ID_{2,3} \oplus ID_{4,2} \oplus ID_{5,1}$]{
    \includegraphics[width=0.2\textwidth]{photo/TIP-diag.pdf}
}
\subfigure[Anti-diagonal parity $GP_6$ to $GP_{11}$, (e.g., $GP_7=ID_{0,0} \oplus ID_{1,1} \oplus ID_{2,2} \oplus ID_{4,3} \oplus ID_{5,4}$)]{
    \includegraphics[width=0.2\textwidth]{photo/TIP-anti-diag.pdf}
}
\caption{Encoding pf TIP-code}
\label{fig-TIP}
\end{figure}

\subsubsection{EVENODD-STAR Approximate Code}
Figure \ref{fig-ap-STAR} shows the construction of Approximate Code ($4,2,4,4$) based on EVENODD \cite{blaum1995evenodd} and STAR \cite{huang2008star}. 
EVENODD is a tipical RAID6 erasure code scheme, while STAR is a 3DFTs extension scheme of EVENODD. In this case, important data blocks are distributed in Layer 0, while unimportant data blocks occupy the rest layers. 
Because the STAR code is constructed just by adding a reverse check chain to the EVENODD code. In this case, we design a global check block to store this check chain, so 3DFTs can be guaranteed.

\begin{figure}[h]
\centering
\includegraphics[width=0.35\textwidth]{photo/AP-EVEN-star-v2.pdf}
\caption{The XOR-based Approximate Code ($4,2,4,4$), constructed based on EVENODD and STAR code. $LP$ represent the local parity and $GP$ represent the global parity.}
\label{fig-ap-STAR}
\end{figure}

\iffalse
\subsection{Fault Tolerance}
In this section we give the fault tolerance of important and unimportant data in the Approximate Code.
We first prove the correctness of our decoding process, and then use a program to 
iterate through all the cases of node failures. Finally, we give the data recovery capability of all cases.
For unimportant data, it only has local parity nodes, so its fault tolerance in Approximate Code($k,r,h,a$) is the same as RS($k,r$), which is any $r$ node failures in $k+r$ nodes in each layer.

For important data, We consider the \emph{full recovery mode} and the \emph{approximate recovery mode} separately. When the number of nodes lost per layer does not exceed $r$, the Approximate Code completely recovers all data in \emph{full recovery mode}. If the damage is more severe, the Approximate Code enters the \emph{approximate recovery mode}.
We still take the Approximate Code ($3, 2, 2, 1/3$) as an example, and discuss the fault tolerance of important and mionor data separately.
Important data nodes can tolerate the loss of any 2r+1 data nodes
At the same time tolerate any r+1 node loss. Only in very rare cases, r+2 nodes are damaged in this way, that is, a data node whose local check node and global check node are damaged at the same time.
First consider only the data nodes:
Second, for the case of all nodes:
\subsection{Reconstruct Cost}
In this section, we introduce the recovery overhead for several common failure cases of Approximate Code. The reconstruct cost is defined as the 
\subsubsection{Single node failure}
When any one data node fails, the reconstruction cost of unimportant data is $k$ read and 1 write, while important data has the cost of $h$ read and 1 write. So the total amount of data that needs to be transferred is 
$$ (1-a)*(k+1) + a*(h+1) $$.

@@

\begin{table}[ht]
\centering 
\caption{Comparison of storage overhead and fault tolerance between Approximate Code, RS and several XOR-based codes.}\label{tab-AS-RS-AP}
\begin{tabular}{|c|c|c|}
\hline
EC & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & Fault Tolerance \\ \hline
RS($k,r$) & $(k+r)/k$ & $r$ \\ \hline
RAID-5($k,1$) & $(k+1)/k$ & 1 \\ \hline
EVENODD($k,2$) & $(k+2)/k$ & 2 \\ \hline
TIP-code/STAR($k,3$) & $(k+r)/k$ & 3 \\ \hline
\begin{tabular}[c]{@{}c@{}}Approximate Code\\ ($k,r,h,s$)\end{tabular} & $\frac {(k+r)s+3-r}{k*s}$ & r to 3 \\ \hline
\end{tabular}
\end{table}

@@

We analyze the nature of the Approximate Code from the following aspects, and the calculation method of the relevant indicators is given in Table \ref{tab-AS-RS-AP}.
\begin{itemize}
    \item Low cost. Approximate code reduces storage overhead by approximating storage strategies. This property is more pronounced for data with a smaller proportion of important data.
    \item High reliability for important data. The Approximate Code guarantees 3DFTs for important data.
    \item Flexibility. The implementation of the Approximate Code can be based on RS, XOR or a mixture of the two.
\end{itemize}

\section{Implementation}\label{Implementation}
\begin{figure}[htb]
\centering
\includegraphics[height = 6.5cm]{photo/implementation-V2.pdf}
\caption{Overview of Approximate Code implementation}
\label{fig-implementation}
\end{figure}

Compared with the traditional scheme that does not consider the meaning of the upper layer data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate layer between the upper layer application and the underlying distributed storage system is necessary to preprocess the data. We call it the approximate storage layer, which include 3 parts: data identification and allocation, encoding and decoding process of Approximate Code and the video fuzzification and recovery.

\subsection{Data Segmentation and Distribution Process}
The identification of data importance can be specified by the upper application as well as automatically determined by the approximate storage layer. We focus on the latter and take video file as an example to introduce our method of automatically distinguishing importance.

For video data encoded by H.264 or similar format, we define I frames as important data, while P frames and B frames as unimportant data based on the analysis in section \ref{video storage}.
\textcolor{orange}{In practical, video data is rarely stored in the original form of H.264 streams (``.264'' files), but is usually storaged in an file such as ``.mp4'' files containing information such as audio. We transcode video files into raw video streams and other data, and we define these non-video data as important because they contain information that the video can't provide and only take up a small amount of space. The feasibility of this definition will be confirmed in} \ref{evaluation}.

@@

The data distribution scheme is shown in the figure \ref{Data-distribution-v2}. We present $\omega_i$ as the $\omega$ of Data(i), and $\omega_{max} = \omega_2$.
For example, Data 3 is represented by blue, and its key segment (10\%) and part of unimportant segment (10\%) are settled in $D_I$.
The main idea of our data distribution method is to guarantee that each GOP has the same proportion of storage in $D_I$ and $D_M$. This method improves flexibility because it is not necessary to maintain a map that marks the location of each GOP, which makes it is easy to add or delete data at any time. Meanwhile, the method is ideal for streaming video data generated in real time by applications such as monitoring.

@@

\subsection{Evaluation methodology}
In our evaluation, we first compare the Approximate Code with the RS code and some XOR-based codes to demonstrate the performance benefits of our solution. Since 3DFTs is a typical erasure code configuration, we use it as a baseline and set the minimum fault tolerance of important data to 3 ($ m + s \geqslant 3 $). We will then demonstrate the quality loss of multimedia data under the traditional and approximate recovery models of severe disk failure to assess the benefits of our approximate storage scheme. We use mathematical analysis and experiments to prove the effectiveness of the Approximate Code.
